Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-15 paper/paper.tex
Last bits

% \begin{figure}[b]
%     \centering
%     \begin{tikzpicture}[scale=0.33]%{{{
%         \begin{scope}
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
% 
%             \draw [very thick] (M1) -- (M2);
%             \draw [very thick] (M2) -- (M4);
%             \draw [very thick] (M3) -- (M5);
%             \draw [color=uofgsandstone!60] (M4) -- (M6);
%             \draw [color=uofgsandstone!60] (M5) -- (M6);
%             \draw [very thick] (M3) -- (M1);
%             \draw [color=uofgsandstone!60] (M6) -- (M7);
%             \draw [color=uofgsandstone!60] (M6) -- (M8);
%             \draw [color=uofgsandstone!60] (M6) -- (M9);
%             \draw [very thick] (M7) -- (M9);
%             \draw [very thick] (M8) -- (M9);
%         \end{scope}
% 
%         \begin{scope}[xshift=5cm]
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, fill=magmapurple, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
% 
%             \draw [very thick] (M1) -- (M2);
%             \draw [very thick] (M2) -- (M4);
%             \draw [very thick] (M3) -- (M5);
%             \draw [color=uofgsandstone!60] (M4) -- (M6);
%             \draw [color=uofgsandstone!60] (M5) -- (M6);
%             \draw [very thick] (M3) -- (M1);
%             \draw [color=uofgsandstone!60] (M6) -- (M7);
%             \draw [very thick] (M7) -- (M8);
%             \draw [very thick] (M8) -- (M9);
%         \end{scope}
% 
%         \begin{scope}[xshift=12cm]
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};
% 
%             \draw [very thick] (M1) -- (M2);
%             \draw [very thick] (M2) -- (M4);
%             \draw [very thick] (M3) -- (M5);
%             \draw [very thick] (M4) -- (M6);
%             \draw [very thick] (M5) -- (M6);
%             \draw [very thick] (M3) -- (M1);
%             \draw [color=uofgsandstone!60] (M6) -- (M7);
%             \draw [very thick] (M6) -- (M8);
%             \draw [color=uofgsandstone!60] (M6) -- (M9);
%             \draw [color=uofgsandstone!60] (M7) -- (M9);
%             \draw [color=uofgsandstone!60] (M8) -- (M9);
%         \end{scope}
% 
%         \begin{scope}[xshift=17cm]
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
%             \node[draw, circle, fill=magmaorange, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
%             \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};
% 
%             \draw [very thick] (M1) -- (M2);
%             \draw [very thick] (M2) -- (M4);
%             \draw [very thick] (M3) -- (M5);
%             \draw [very thick] (M4) -- (M6);
%             \draw [very thick] (M5) -- (M6);
%             \draw [very thick] (M3) -- (M1);
%             \draw [very thick] (M6) -- (M7);
%             \draw [draw=uofgsandstone!60] (M7) -- (M8);
%             \draw [draw=uofgsandstone!60] (M8) -- (M9);
%         \end{scope}
% \end{tikzpicture}
% \caption{A maximum common subgraph of the first two graphs has eight vertices, shaded. A maximum
% common \emph{connected} subgraph, shown on the right, has only seven vertices.}
% \label{figure:mcsexample}
% \end{figure}

@@

Finding a maximum common subgraph is the key step in measuring the similarity or difference between
two graphs \citep{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,o:Kriege15}: to determine
the difference between two graphs, we find what they have in common, and then take everything left
over. Because of this, maximum common subgraph problems frequently arise in biology and chemistry
\citep{DBLP:journals/jcamd/RaymondW02a,o:EhrlichR11,DBLP:journals/dam/GayFMSS14} where graphs
represent molecules or reactions, and also in computer vision
\citep{DBLP:journals/jair/CookH94,DBLP:conf/gbrpr/CombierDS13}, computer-aided manufacturing
\citep{o:LuoWSN17}, crisis management \citep{o:DelavalladeFLL16}, the analysis of programs and
malware \citep{DBLP:conf/icics/GaoRS08,DBLP:journals/compsec/ParkRS13}, social network analysis
\citep{DBLP:journals/tkde/FangYZZ15}, graph database query explanations
\citep{DBLP:journals/jcss/VasilyevaTBL16}, and in character recognition problems
\citep{DBLP:journals/pr/LuRS91}.  A common variant of the problem requires a largest
\emph{connected} subgraph
\citep{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,o:EhrlichR11,o:LuoWSN17}.

% As illustrated in \cref{figure:mcsexample}, a maximum common connected subgraph cannot be determined
% from the maximum common subgraph.

>>>>

\begin{figure}[b]
    \centering
    \begin{tikzpicture}[scale=0.25]%{{{
        \begin{scope}
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [color=uofgsandstone!60] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [very thick] (M7) -- (M9);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=5cm]
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmapurple, inner sep=0.2pt, font=\small] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [color=uofgsandstone!60] (M4) -- (M6);
            \draw [color=uofgsandstone!60] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M7) -- (M8);
            \draw [very thick] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=12cm]
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [color=uofgsandstone!60] (M6) -- (M7);
            \draw [very thick] (M6) -- (M8);
            \draw [color=uofgsandstone!60] (M6) -- (M9);
            \draw [color=uofgsandstone!60] (M7) -- (M9);
            \draw [color=uofgsandstone!60] (M8) -- (M9);
        \end{scope}

        \begin{scope}[xshift=17cm]
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=magmaorange, inner sep=0.2pt, font=\small] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!60, fill=white, inner sep=0.2pt, font=\small] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

            \draw [very thick] (M1) -- (M2);
            \draw [very thick] (M2) -- (M4);
            \draw [very thick] (M3) -- (M5);
            \draw [very thick] (M4) -- (M6);
            \draw [very thick] (M5) -- (M6);
            \draw [very thick] (M3) -- (M1);
            \draw [very thick] (M6) -- (M7);
            \draw [draw=uofgsandstone!60] (M7) -- (M8);
            \draw [draw=uofgsandstone!60] (M8) -- (M9);
        \end{scope}
\end{tikzpicture}
\caption{A maximum common subgraph of the first two graphs has eight vertices, shaded. A maximum
common \emph{connected} subgraph, shown on the right, has only seven vertices.}
\label{figure:mcsexample}
\end{figure}

@@

Finding a maximum common subgraph is the key step in measuring the similarity or difference between
two graphs \citep{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,o:Kriege15}: to determine
the difference between two graphs, we find what they have in common, and then take everything left
over. Because of this, maximum common subgraph problems frequently arise in biology and chemistry
\citep{DBLP:journals/jcamd/RaymondW02a,o:EhrlichR11,DBLP:journals/dam/GayFMSS14} where graphs
represent molecules or reactions, and also in computer vision
\citep{DBLP:journals/jair/CookH94,DBLP:conf/gbrpr/CombierDS13}, computer-aided manufacturing
\citep{o:LuoWSN17}, crisis management \citep{o:DelavalladeFLL16}, the analysis of programs and
malware \citep{DBLP:conf/icics/GaoRS08,DBLP:journals/compsec/ParkRS13}, and social network analysis
\citep{DBLP:journals/tkde/FangYZZ15}. A common variant of the problem requires a largest
\emph{connected} subgraph
\citep{DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,o:EhrlichR11,o:LuoWSN17}.
As illustrated in \cref{figure:mcsexample}, a maximum common connected subgraph cannot be determined
from the maximum common subgraph.
